Scikit-learn: machine learning without learning the machinery

### 2014-05-18 article.tex
Finish intro to ML

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 features, including wage, number of years of education and of work
experience, on 534 individuals --samples in machine-learning
jargon. This data
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties machine learning.
The samples are very irregularly distributed, as most individuals
finished their education after high-school. As a result, they are gapping
holes in the 2D plot education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given education and work experience wages vary widely. This variability
can probably be explained with missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, Random Forests, to try to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined.

% Show an example of learning, first with random forest, and introduce
% overfit, then with svms, and discuss model complexity and use linear
% models to link to convention statistics. Conclude with the difference
% with 1D and 2D, and introduce the curse of dimensionality.
Discuss what we can learn from the wages examples. Introduce concepts of
overfitting, model complexity

@@

@@

    \caption{Wage prediction from years of work experience and education,
    using a linear SVM.}
\end{figure}

>>>>

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data \cite{elemstatlearn}. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 features, including wage, number of years of education and of work
experience, on 534 individuals --samples in machine-learning
jargon. This data
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties machine learning.
The samples are very irregularly distributed, as most individuals
finished their education after high-school. As a result, they are gapping
holes in the 2D plot education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given education and work experience wages vary widely. This variability
can probably be explained with missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, Random Forests, to try to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined. The patchy square appearance of the prediction is due to the
inners of the algorithm, and it illustrates the corresponding
extrapolation mechanism. The predictions fit the data very; maybe too
well, as, on the prediction solely from the years of education (left of
the figure), it is hard to believe in the bump at 5 years. This bump is
probably a classic case of \emph{overfit}: the algorithm is learning its
prediction from noise in the data. As a result, the prediction error on
new data will be significantly different than that measured on the
training data.

@@

% then with svms, and discuss model complexity and use linear
% models to link to convention statistics. Conclude with the difference
% with 1D and 2D, and introduce the curse of dimensionality.
%overfitting, model complexity

On Fig.\,\ref{fig:linear_svm}, we use another popular machine-learning
algorithm, linear Support Vector Machines (SVMs). Unlike random forests,
it can only learn decisions made with linear functions. It is said that
it has a lower \emph{model complexity}, because the number of parameters
to learn from the data is much smaller. The risk here is to
\emph{underfit}: not fully use the richness of the data, that may not be
following a linear law. The art of machine learning consists in choosing
the right family of algorithms (or models) to describe the data well and
find the sweet spot between under and over fit. As the number of features
describing the data grows, the number of parameters to learn grows, and
thus the risk of overfit increases. This core difficulty is known as the
\emph{curse of dimensionality}.

@@

    \caption{Wage prediction from years of work experience and education,
    using a linear SVM.\label{fig:linear_svm}}
\end{figure}
